Here start the section for clearing algo. Citation example: \cite{kenyon2002high}.

\begin{definition*}[\textbf{Futures Positions: Long and Short}]
  A futures contract is a commitment between two or more counterparties who agree to
  engage in a transaction at a later date and a prespecified price. The contract gives
  one party the right to buy/sell the underlying asset for a specific price at a specific
  date in the future. We call this specific price a futures price.
  Depending on whether we acquire the right to buy or sell, we refer to our
  position as a long or a short position, respectively. The value of the contract at
  the outset is zero as both counterparties have the same probability of making
  gains at that point. No cash changes hands as a result.
  Thus, the long position represents the right to buy the underlying asset at a
  specific futures price. The short position gives its holder the right to sell the
  underlying asset at a futures price sometime in the future. Futures (and
  forward) contracts can be written on a variety of underlying assets such as
  commodities, foreign exchange, short-term debt, and stock indices.
\end{definition*}

\begin{definition}[\textbf{Status Futures Positions}]

Let $\bLf$ be a set of characters and\, $\bl=(l_{1}, l_{2}, l_{3}, l_{4}),\bs=(s_{1}, s_{2}, s_{3}, s_{4})\in\bLf^4$
status for future postions defined by mean

\begin{align}
\begin{bmatrix}
        \,l_{1} \\
        \,l_{2} \\
        \,l_{3} \\
        \,l_{4}
\end{bmatrix}
&=
\begin{bmatrix}
        \textsc{Long Position Increased} \\
        \textsc{Open Long Position} \\
        \textsc{Long Position Netted Partly\,\,} \\
        \textsc{Long Position Netted} \\ 
\end{bmatrix}
\\
\begin{bmatrix}
        s_{1} \\
        s_{2} \\
        s_{3} \\
        s_{4}
\end{bmatrix}
&=
\begin{bmatrix}
        \textsc{Short Position Increased} \\
        \textsc{Open Short Position} \\
        \textsc{Short Position Netted Partly} \\
        \textsc{Short Position Netted} \\ 
\end{bmatrix}
\end{align}

\end{definition}
